Numerical analysis of the influence of magnetic field waveforms on the performance of active magnetic regenerators

### 2019-09-17 PaperMagneticProfiles_JBSMSE.tex
Edit section in ramp results.

Based on the better performance of the instantaneous profile, the ramp profile is assumed as a suitable target profile for the design of magnetic refrigerators, and will be analyzed in this section.

Moving towards a more realistic model, casing losses are included, using the model from \cite{bib:trevizoli16_perfor_model}. The bed is enclosed in a solid casing of thickness $h\ped{csg}$, and two air layers of thickness $h\ped{air}$ separate \textcolor{black}{the AMR and its casing} from the inner and outer \textcolor{black}{magnet} cylinders.

@@

\nomenclature[ia]{air}{air layer between magnets and regenerators}
\nomenclature[ic]{csg}{regenerator casing}

Preliminary analyses \textcolor{black}{carried out by} \cite{bib:peixer17-perfor-amrs} using the losses model described in \autoref{sec:model-casing-loss} showed that a stainless steel casing \textcolor{black}{with a} thickness \textcolor{black}{of} $h\ped{csg} = \SI{0.5}{\mm}$ is thick enough to ensure mechanical integrity and easy manufacturing, while being thin enough to accommodate the material \textcolor{black}{with a low} thermal conductivity.

@@

\begin{table}[!ht]
  \centering
  \begin{tabular}{c|c}
\hline
    \textbf{Parameter} & \textbf{Value} \\
\hline
$R\ped{o}$ & \SI{40}{\mm} \\
$W\ped{r}$ & \SI{30}{\mm} \\
$L\ped{r}$ & \SI{85}{\mm} \\
$N\ped{r}$ & \num{8} \\
$N\ped{v}$ & \num{16} \\
$f$ & \SI{1}{\hertz} \\
$\th$ & \SI{305.5}{\kelvin} = \SI{32.5}{\celsius} \\
$\tc$ & \SI{270.5}{\kelvin} = \SI{-2.5}{\celsius} \\
$D\ped{p}$ & \SI{350}{\micro\meter} \\
$h\ped{csg}$ & \SI{0.5}{\mm} \\
$h\ped{air}$ & \SI{1}{\mm} \\
Casing material & Stainless steel \\
Number of layers & \num{3} \\
Curie temperatures of each layer & \num{273}, \num{283}, \SI{290}{\kelvin} \\ 
Length fractions of each layer & \num{20}, \num{20}, \SI{60}{\percent}\\
\hline
  \end{tabular}
  \caption{Fixed parameters for the AMR simulations used in this chapter}
  \label{tab:params-ramp}
\end{table}

\subsubsection{Synchronization between \textcolor{black}{the} fluid flow and magnetic profiles}
\label{sec:synchr-betw-fluid}

A central point of this Thesis is \textcolor{black}{related to} the importance of two characteristic waveforms, the fluid flow and magnetic profiles, \textcolor{black}{and how they affect} the performance of a magnetic refrigerator. Several works have independently investigated the synchronization between these profiles \cite{bib:bjoerk11_amr,bib:nakashima17-exper}. Here, \textcolor{black}{the} focus is  on the parameterization of these waveforms and \textcolor{black}{the} characerization of an AMR system with these parameters, in particular the blow fraction (cf. \autoref{sec:inst-fluid-flow}) and the magnetization fraction (cf. \autoref{sec:ramp-magn-prof}). Figure~\ref{fig:ramp-inst} shows the two profiles that will be used in this section.

@@

Regarding the magnetic profile, the \textcolor{black}{magnitude of the} high value will be varied to investigate the performance of the AMR system, while the minimum will be kept at $\bmin = \SI{0.05}{\tesla}$. Ideally, this value \textcolor{black}{should be nil}, but it is \textcolor{black}{difficult} to achieve complete flux insulation in the low field region, so \textcolor{black}{a finite value of the} minimum field is \textcolor{black}{adopted}.

@@

Figure~\ref{fig:Qc_COP_curves_phi40} shows the cooling capacity and coefficient of performance of the AMR system for a fixed utilization factor of \num{0.4} and for a magnetic profile with \textcolor{black}{a} maximum at \SI{1.3}{\tesla}, for \textcolor{black}{variable} blow and magnetization fractions. \textcolor{black}{To facilitate the analysis, the} results are plotted in terms of the ratio $\nicefrac{F\ped{M}}{F\ped{B}}$, with curves for different \textcolor{black}{values of} $F\ped{B}$. It is clear \textcolor{black}{that both the cooling capacity and the coefficient of performance exhibit a peak at} $F\ped{M} = F\ped{B}$. Moreover,  \textcolor{black}{to the right of the peak, i.e., for higher values of $F\ped{M}$, the}  reduction \textcolor{black}{of} both \textcolor{black}{performance} metrics \textcolor{black}{is} slower, meaning it is better to have a magnetization plateau wider than the fluid flow plateau, thus confirming the conclusions \textcolor{black}{of} \autoref{cha:exper-invest-fluid}.

The reduction in performance for $F\ped{M} > F\ped{B}$ \textcolor{black}{can be explained by an increase in} heat leakage through the casing, as the solid begins to lose energy to the environment \textcolor{black}{when} the fluid is not flowing. For $F\ped{M} < F\ped{B}$, the effect \textcolor{black}{discussed in} \autoref{sec:results-discussions} is present: the fluid begins to flow when the solid is not totally warmed up, losing effectiveness.

@@

The influence of \textcolor{black}{the} utilization is demonstrated in \autoref{fig:Qc_curves_ramp_phi}, where the cooling capacity \textcolor{black}{is} plotted for different utilization factors. For increasing $\Phi$ in this range, not only do the overall values of cooling capacity increase, but also the importance of choosing the blow fraction becomes clearer. In \textcolor{black}{these ranges} of utilization and blow fraction,  the cooling capacity increases because the higher transfer rate associated with higher flow rates \textcolor{black}{dominates} over the loss of regenerator effectiveness.

@@

\textcolor{black}{All} previous results assumed a fixed regenerator geometry, with the goal of identifying the optimal fluid and magnetic profile parameters. \textcolor{black}{It became clear that the} magnetization fraction should be as large as possible, but that makes it more difficult to design a magnetic circuit \textcolor{black}{based on} permanent magnets. The value of $F\ped{M} = \SI{70}{\percent}$ is then chosen as a compromise, with \textcolor{black}{a corresponding} $F\ped{B} = F\ped{M}$. The mean value of \textcolor{black}{the} utilization factor of $\Phi = 0.4$ is also chosen as reference in the next results.

In this section, the \textcolor{black}{effect of the} regenerator height is \textcolor{black}{evaluated. The results will complement those for the} air gap height that will be shown in \autoref{cha:design-optim-magn} concerning the design of the magnetic circuit. The importance of the air gap height as a coupling \textcolor{black}{parameter} between the geometric design of the regenerators and the magnetic circuit was explored using a simplified model in \autoref{sec:performance-an-amr} and using the instantaneous magnetic profile in \autoref{sec:deta-analys-inst}. The results \textcolor{black}{to be} shown \textcolor{black}{here} use the magnetic \textcolor{black}{ramp} profile \textcolor{black}{studied in depth in} this present chapter.

>>>>

Based on the better performance of the instantaneous profile, the ramp profile is assumed as a suitable target profile for the design of magnetic refrigerators, and will be analyzed in this section, representing the second stage in the analysis of magnetic profiles.

Moving towards a more realistic model, casing losses are included, using the model from \cite{bib:trevizoli16_perfor_model}. The bed is enclosed in a solid casing of thickness $h\ped{csg}$, and two air layers of thickness $h\ped{air}$ separate \textcolor{black}{the AMR and its casing} from the inner and outer \textcolor{black}{magnet} cylinders, as shown in \autoref{fig:amr-casing}. These magnetic cylinders can be designed to yield the desired magnetic profiles, as will be shown in future studies by our group.

@@

\nomenclature[ia]{air}{air layer between magnets and regenerators}

Preliminary analyses \textcolor{black}{carried out by} \cite{bib:peixer17-perfor-amrs} showed that a stainless steel casing \textcolor{black}{with a} thickness \textcolor{black}{of} $h\ped{csg} = \SI{0.5}{\mm}$ is thick enough to ensure mechanical integrity and easy manufacturing, while being thin enough to accommodate the material \textcolor{black}{with a low} thermal conductivity.

@@

\begin{table}[!ht]
  \centering
  \begin{tabular}{c|c}
\hline
    \textbf{Parameter} & \textbf{Value} \\
\hline
$R\ped{o}$ & \SI{40}{\mm} \\
$W\ped{r}$ & \SI{30}{\mm} \\
$L\ped{r}$ & \SI{85}{\mm} \\
$N\ped{r}$ & \num{8} \\
$N\ped{v}$ & \num{16} \\
$f$ & \SI{1}{\hertz} \\
$T\ped{H}$ & \SI{305.5}{\kelvin} = \SI{32.5}{\celsius} \\
$\tc$ & \SI{270.5}{\kelvin} = \SI{-2.5}{\celsius} \\
$D\ped{p}$ & \SI{350}{\micro\meter} \\
$h\ped{csg}$ & \SI{0.5}{\mm} \\
$h\ped{air}$ & \SI{1}{\mm} \\
Casing material & Stainless steel \\
Number of layers & \num{3} \\
Curie temperatures of each layer & \num{273}, \num{283}, \SI{290}{\kelvin} \\ 
Length fractions of each layer & \num{20}, \num{20}, \SI{60}{\percent}\\
\hline
  \end{tabular}
  \caption{Fixed parameters for the AMR simulations used in this chapter}
  \label{tab:params-ramp}
\end{table}

 Figure~\ref{fig:ramp-inst} shows the two profiles that will be used in this section and how they are synchronized. Regarding the magnetic profile, the \textcolor{black}{magnitude of the} high value will be varied to investigate the performance of the AMR system, while the minimum will be kept at $\bmin = \SI{0.05}{\tesla}$.

@@

@@

Figure~\ref{fig:Qc_COP_curves_phi40} shows the cooling capacity and coefficient of performance of the AMR system for a fixed utilization factor of \num{0.4} and for a magnetic profile with \textcolor{black}{a} maximum at \SI{1.3}{\tesla}, for \textcolor{black}{variable} blow and magnetization fractions. \textcolor{black}{To facilitate the analysis, the} results are plotted in terms of the ratio $\nicefrac{F\ped{M}}{F\ped{B}}$, with curves for different \textcolor{black}{values of} $F\ped{B}$. It is clear \textcolor{black}{that both the cooling capacity and the coefficient of performance exhibit a peak at} $F\ped{M} = F\ped{B}$. Moreover,  \textcolor{black}{to the right of the peak, i.e., for higher values of $F\ped{M}$, the}  reduction \textcolor{black}{of} both \textcolor{black}{performance} metrics \textcolor{black}{is} slower, meaning it is better to have a magnetization plateau wider than the fluid flow plateau

The reduction in performance for $F\ped{M} > F\ped{B}$ \textcolor{black}{can be explained by an increase in} heat leakage through the casing, as the solid begins to lose energy to the environment \textcolor{black}{when} the fluid is not flowing. For $F\ped{M} < F\ped{B}$,  the fluid begins to flow when the solid is not totally warmed up, losing effectiveness.

@@

The influence of utilization is demonstrated in \autoref{fig:Qc_curves_ramp_phi}, where the cooling capacity \textcolor{black}{is} plotted for different utilization factors. For increasing $\Phi$ in this range, not only do the overall values of cooling capacity increase, but also the importance of choosing the blow fraction becomes clearer. In \textcolor{black}{these ranges} of utilization and blow fraction,  the cooling capacity increases because the higher transfer rate associated with higher flow rates \textcolor{black}{dominates} over the loss of regenerator effectiveness.

@@

\textcolor{black}{All} previous results assumed a fixed regenerator geometry, with the goal of identifying the optimal fluid and magnetic profile parameters. \textcolor{black}{It became clear that the} magnetization fraction should be as large as possible, but that raises some challenges in realizing abrupt changes in the magnetic field. The value of $F\ped{M} = \SI{70}{\percent}$ is then chosen as a compromise, with \textcolor{black}{a corresponding} $F\ped{B} = F\ped{M}$. The mean value of \textcolor{black}{the} utilization factor of $\Phi = 0.4$ is also chosen as reference in the next results.
